\chapter{Conclusion and Future Work}
Visualization systems help us summarize and explore the ever expanding amount of
information we live with today. In this work we address a particular problem
domain of trying to make sense of a large quantity of text. Unlike traditional
InfoVis systems that rely on abstract representations, we explore different ways
to encoding underlying semantics on forms that are familiar to viewers. 

In this section we summarize our result findings, the limitations of our
application, and discuss avenues for future work.

\section{Conclusion}
Our main contribution in this work is an integrated approach for doing text
analytics for documents that contain both spatial and non-spatial data. We
developed a scoring function that maps abstract semantics onto \threed models as
stylistic graphical effects. Our goal is to use this approach to producing a
more engaging visualization by depicting these objects as they appear in life,
allowing people to formulate queries based on their familiarity with the objects
and real world metaphors.

In this thesis, we applied our methods to analyze a large collection of vehicle
complaint reports from the NHTSA database. We leveraged WordNet database to
create a vocabulary of vehicle entity, we then score each document based on
occurrence and co-occurrence relations among the different vehicle entities.
We also take into consideration time and organizational hierarchy dimensions. We
applied the entity scores onto a \threed vehicle model using NPR techniques to
emphasis importance. Finally we created interactive widgets for exploration of
the dataset. Our intended audience are vehicle owners and potential consumers
whom have a stake in the safety and reliability of their vehicles.


As a necessary step towards validating our design and hypothesis, we ran a user
study to see if people can accurately interpret the visualization, we also
solicited qualitative feedback from study participants. Our study showed that
(need results to put in here)


\section{Limitations}
In this thesis, we have presented a working prototype of our ideas. However,
there are still some challenges and limitations. The limitations of our
prototype falls primarily into two categories: language processing and graphical
representation. In this section we will discuss what they are and possible
solutions.

From a language perspective, our system of parsing is quite simplistic as we are
only taking into account word frequencies. Casual relations are inferred with
co-occurring entities, however a more precise method would use grammatical
structures to infer relations. While we have made early attempt at extracting
dependency relations, it did not yield fruitful result due to many grammatically
incorrect sentences within the document collection, although a different text
corpus may benefit from this approach. We also only looked at nouns, but verbs
and other domain specific terms can attribute themselves to specific components,
including them in our vocabulary would have increased our coverage.

In terms of graphical representations, occlusion still presents an issue,
especially in densely packed areas. These areas makes interactions difficult.
While the heatmaps provide an easy alternative for selection, it does not solve
perceptual difficulties in trying to uniquely identify an object in the
visualization. Zooming into the scene, or changing the lens' depth only
partially solve the problem as both method require very fine tuning from the
viewer. Alternative selecting approaches, such as selecting by importance score,
or other heuristic may help. More advanced graphical techniques such as exploded
views would be able to push objects away from each other, avoiding occlusion in
the first place but at a possible risk of distorting the overall context.


\section{Future Work}
While we have explored different mappings in terms of language and graphics,
there is another aspect that we have left unexplored. The social aspect of
computing is a prominent topic today and worthwhile for further investigation.
How one would go about annotating, sharing and searching for other people's
findings are tasks that go beyond the individual that can help help the entire
community.

As hinted in limitations section, more robust language processing would be very
desirable. In particular, it would be interesting to look at sentiment analysis.
The capability to quantity positive or negative connotations would be beneficial
in understanding how people perceive certain objects.

Ambient settings is another possible area for future work, one can imaging using
camera planning algorithms to conduct a virtual tour of the entities while not
receiving input interactions. The said tour can be used to raise awareness of
particular features and highlight trends. The tour could be interrupted when a
person starts interacting with the display.

Lastly, while in this thesis we have primarily looked at the vehicle domain. We
believe our approach is generalizable to other problems. Other analytical tasks
that relates text to physical productions may benefit from our approach. For
example, it is not hard to imagine using our approach to visualize airplane
maintenance records, where we can use it to identify past, or perhaps even
forecast maintenance issues.
